\documentclass[letterpaper,10pt]{article}

\usepackage{listings}
\usepackage{color}
\usepackage{tikz}

\setlength{\headheight}{0in}
\setlength{\marginparsep}{0in}
\setlength{\footskip}{0in}
\setlength{\headsep}{0in}
\setlength{\marginparwidth}{0in}
\setlength{\marginparpush}{0in}
\setlength{\voffset}{0in}
\setlength{\hoffset}{-1in}
\setlength{\voffset}{-1in}
\setlength{\oddsidemargin}{0.75in}
\setlength{\evensidemargin}{0.75in}
\setlength{\topmargin}{0.75in}
\setlength{\textheight}{9.5in}
\setlength{\textwidth}{7in}
\setlength{\parindent}{0in}
\setlength{\parskip}{10pt} %change this to match font size

\pagestyle{empty}
\definecolor{gray}{gray}{0.75}
\usetikzlibrary{shapes,arrows,calc}
\lstset{numbers=left,backgroundcolor=\color{gray},frame=single}

% define block styles
\tikzstyle{line} = [draw, -latex']
\tikzstyle{block} = [draw, rectangle, text centered, minimum height=2em]
\tikzstyle{mlblock} = [draw, rectangle, text width=10em, text centered, minimum height=2em]
\tikzstyle{decision} = [draw, diamond, text width=4.5em, text centered, node distance=3cm, inner sep=0pt]
\tikzstyle{cloud} = [draw, rectangle, text centered, rounded corners, minimum height=2em]

\begin{document}
    Albert Chang and Nipun Chopra\\
    CSE-380 A6\\
    University at Buffalo\\
    Dr. Kris Schindler\\
    February 22, 2011\\
    \textit{Lab 3 Documentation}

    The objective of Lab 3 was to write five subroutines, named
    \textit{read\_string}, \textit{output\_string}, \textit{mod},
    \textit{uart\_init}, and \textit{lab3}. Ultimately, the goal of all
    subroutines created a program that provided the modulo of two numbers
    provided by the user. It would give immediate feedback by displaying what
    the user input through the serial. The range of numbers was also limited
    between 0 and 99,999.

    The majority of the lab was already done through previous lab objectives.
    The \textit{mod} routine required only one line to be changed in the
    \textit{division} routine from lab 2, so that it returned the remainder
    instead of the quotient. The \textit{read\_character} and
    \textit{output\_character} routines were made in the first part of this lab.
    And finally, the \textit{uart\_init} routine was a simple rewrite of the
    \textit{serial\_init} function from the C wrapper that was provided. The
    only codes that needed to be split up between the two were the
    \textit{read\_string}, \textit{output\_string}, and \textit{lab3}  routines.
    Albert wrote the \textit{output\_string} and \textit{lab3} routines, while
    Nipun wrote the \textit{read\_string} routine.

    Although it would've been more efficient for subroutines to perform checks,
    it was decided that  the checks would be placed in the main \textit{lab3}
    routine. This would ensure the subroutines keep to their functions, never
    leaving the scope of the job they were to perform. What we gain is the
    routines are more portable. The other routines can be used by any other
    routines. If we wanted to reuse these pieces of code, the custom checks may
    need to be changed or remove completely to be compatible.
    
    The trade-off for this added portability is there are added branching
    instructions and there are added instructions for constructing and
    destructing strings for analysis.

    In order to convert a string to an integer, we iterate through the string,
    converting each digit from the ascii value to the integer it represents.
    As we iterate, to combine the other digits, multiply the current integer
    by 10, and add the next one.

    Converting from integer to string needed a little more work. The lowest
    digit is extracted by taking the modulus of the number by 10, and dividing
    it by 10.

    \input{main_flow}

    The \textit{uart\_init} routine was a simple linear routine. It was a direct
    translation of the \textit{serial\_init} function in the c wrapper.
    \input{uart_init_flow}

    The \textit{division} flowchart was simply copied over from Lab 2 to use
    for the \textit{mod} flowchart. Note that although the flowchart is
    unchanged, there was a line that was changed so that it returned the
    remainder instead of the quotient. An additional return was added on
    to help with converting a string to integer, allowing the routine to return
    both the modulo and the division between the two numbers.

    \input{division_flow}

    The \textit{read\_character} and \textit{output\_character} flowcharts both
    came from lecture.

    \begin{minipage}{0.5\linewidth}
        \input{read_char_flow}
    \end{minipage}%
    \begin{minipage}{0.5\linewidth}
        \input{output_char_flow}
    \end{minipage}

    The \textit{output\_string} routine basically iterates bytes in the given
    address until a null character is met. It passes each byte to the
    \textit{output\_character} routine.
    \input{output_string_flow}

    The \textit{read\_string} routine was a little more complicated than
    \textit{output\_string}. First, it it gives direct feedback. Every time a
    character is read in from \textit{read\_character}, it outputs the character
    through \textit{output\_character}. It does this regardless of the input.
    However, in checks for and stores only printable characters. So the user
    would be able to hit the backspace, and the UART will respond expectedly,
    but it won't store the backspace into memory. This is the action taken with
    all non-printable characters. Finally, when the user hits enter, it creates
    a nice output by printing out a new line and carriage return.
    \input{read_string_flow}

    mod\_ui\_wrapper.c
    \lstinputlisting[language=C]{../mod_ui_wrapper.c}

    \newpage

    mod\_ui.s
    \lstinputlisting{../mod_ui.s}

\end{document}
